Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
wrote most of g=0 main theorem pf

Now let us consider the case when $\delta \geq 2$. In this case,
$\halfcan$ is an effective divisor.

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
~\ref{lem:g_0_admissible_cases}. In other words, one of the base
cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
$e_i = e_i'$ otherwise. If $r > 5$, then we can use Proposition
~\ref{prop:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$, since the
saturation in this case is equal to $3$.

We know that each base case satisfies all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max (5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.

>>>>

Now let us consider the case when $\delta \geq 2$. In this case,
$\halfcan$ is an effective divisor. \todo{need to do this case}

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
and not one of the exceptional cases in Table
~\ref{table:g_0_exceptional}.

If $r > 5$, then we can use Proposition
~\ref{prop:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
this case satisfies all of the conditions by Lemma \todo{need this case
to satisfy conditions for adding points}, the
immediate consequence of parts (a) and (c) of Proposition
~\ref{prop:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
\ldots, e_r')$ with relations generated up to degree $2e$.
Furthermore, Proposition ~\ref{prop:sat_three_induction}(d)
implies that these cases satisfy all of the hypotheses of Theorem
~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $\sigma', J$
where $\sigma'$ has $r$ many ramification points all of order $3$
and $J = \{1, \ldots, r\}$. If $r \leq 5$, then $\sigma$ ``lies
above'' one of the base cases of Lemma ~\ref{lem:g_0_admissible_cases}.
In either case, there is a $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$ satisfying the property that for all $i \in J$,
$e_i \geq e_i'$ and $e_i = e_i'$ otherwise where $(\sigma', J)$
is either a base case from Lemma ~\ref{lem:g_0_admissible_cases}
or the case from $r > 5$.

All such base cases satisfy all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.
